Future challenges for Research Software Engineering

### 2025-04-14 future_challenges_for_RSEng.tex
elaborate intro parts

% Main part of your article
% =========================
\section{Introduction}
This opinion article stems from a Bof session at deRSE25 in Karlsruhe\cite{Goth2025EndRSEng}.
Therefore it stems from a discussion among the participants of this workshop and hence cannot claim that it represents the entire deRSE community.
Nevertheless we hope, that we succeeded in writing up something that
\begin{itemize}
\item you like to read,
\item gives you something to think about,
\item motivates you to work on creating this better future.
\end{itemize}

- Why do we do this

@@

\section{Aspects of this future}
It is diffcult to structure the different aspects in describing the future. We decided for the following

\subsection{What do we want to have achieved by 2035}

>>>>

% Main part of your article
% =========================
\section{Introduction}
This opinion article stems from a Bof session at deRSE25 in Karlsruhe\cite{Goth2025EndRSEng}.
Therefore it stems from a discussion among the participants of this workshop and hence cannot claim that it represents the entire deRSE community.
Nevertheless we hope, that we succeeded in writing up something that
\begin{itemize}
\item you like to read,
\item gives you something to think about,
\item motivates you to work on creating this better future.
\end{itemize}
In order to structure the discussion, we decided on a imaginable setting ten years from now. 
In this world we will consider the dimensions of 
\begin{itemize}
\item Evolution of the term RSEs
\item The development of academic institutions
\item How will academic education have transformed by then
\item Ethics and social considerations
\end{itemize}
In each aspect we will quickly summarise on what we want to have achieved by then, and what will be the challenges that arise from that.

@@

\section{Aspects of this future}
It is difficult to structure the different aspects in describing the future. We decided to consider
\begin{itemize}
\item The evolution of the term RSE
\item How is education reshaped by the digital transformation
\item What will the impact of AI be to the work of RSEs?
\item Changes to the Academic Institutions
\item Ethics and social considerations
\item Impact of alternate career paths for RTPs
\end{itemize}

%\subsection{What do we want to have achieved by 2035}
